Co-moving stars in \textsl{Gaia DR1}: a catalog of genuine comoving star pairs from low-resolution spectroscopic follow-up

### 2017-06-05 paper/comoving-followup.tex
todo
fix software section

To derive radial velocities for each source, we then measure the (wavelength)
line centroid of \Ha\ in each corrected spectrum.
We model the absorption line using a pixel-convolved Voigt profile and again use
a Gaussian process for the background model (with the same parameterizations as
described above).
We now use \lbfgsb\ optimization and the resulting maximum-likelihood parameters
to initialize a Markov Chain Monte Carlo (MCMC) sampling of the posterior
probability distribution over the 6 parameters: $\ln |A|$, $x_0$, $\ln\sigma_G$,
$\ln\gamma_L$, $\ln\sigma_{3/2}$, and $\ln\rho_{3/2}$.
The linear amplitude, $A$, is assumed to be negative (i.e. \Ha\ is assumed to be
an absorption feature) and is computed from the corresponding parameter as $A =
-\exp(\ln |A|)$.
We use uniform priors on all parameters except $\ln\rho_{3/2}$, for which we use
a Gaussian; prior parameters are specified in \tablename~\ref{tbl:prior-bounds}.
\figurename~\ref{fig:Halpha-mcmc} shows \todo{mcmc shite}.
With the resulting posterior samples, we compute the median and median absolute
deviation (MAD) of the marginal distribution over line centroid, $x_0$.
We use the MAD to estimate the standard deviation ($\sigma \approx 1.5~{\rm
MAD}$, assuming the samples are Gaussian distributed) of the samples and find
that the typical velocity \emph{precision} from measuring the centroid of \Ha\ is between $2$--$10~\kms$ \todo{double check numbers}.

@@

\software{
The code used in this project is available from
\url{https://github.com/adrn/GaiaPairsFollowup} under the MIT open-source
software license.
This research utilized the following open-source \python\ packages:
    \package{Astropy} (\citealt{Astropy-Collaboration:2013}),
    \package{astroquery} (\citealt{Ginsburg:2016}),
    \package{ccdproc} (\citealt{Craig:2015}),
    \package{celerite} (\citealt{Foreman-Mackey:2017}),
    \package{IPython} (\citealt{Perez:2007}),
    \package{matplotlib} (\citealt{Hunter:2007}),
    \package{numpy} (\citealt{Van-der-Walt:2011}),
    \package{scipy} (\url{https://www.scipy.org/}),
    \package{sqlalchemy} (\url{https://www.sqlalchemy.org/})
}
This work additionally used the Gaia science archive
(\url{https://gea.esac.esa.int/archive/}).

>>>>

To derive radial velocities for each source, we then measure the (wavelength)
line centroid of \Ha\ in each corrected spectrum.
We model the absorption line using a pixel-convolved Voigt profile and again use
a Gaussian process for the background model (with the same parameterizations as
described above).
We now use \lbfgsb\ optimization and the resulting maximum-likelihood parameters
to initialize a Markov Chain Monte Carlo (MCMC) sampling of the posterior
probability distribution over the 6 parameters: $\ln |A|$, $x_0$, $\ln\sigma_G$,
$\ln\gamma_L$, $\ln\sigma_{3/2}$, and $\ln\rho_{3/2}$.
The linear amplitude, $A$, is assumed to be negative (i.e. \Ha\ is assumed to be
an absorption feature) and is computed from the corresponding parameter as $A =
-\exp(\ln |A|)$.
We use uniform priors on all parameters except $\ln\rho_{3/2}$, for which we use
a Gaussian; prior parameters are specified in \tablename~\ref{tbl:prior-bounds}.
\todo{Explain MCMC, emcee, steps, etc.}
\figurename~\ref{fig:Halpha-mcmc} shows \todo{mcmc shite}.
With the resulting posterior samples, we compute the median and median absolute
deviation (MAD) of the marginal distribution over line centroid, $x_0$.
We use the MAD to estimate the standard deviation ($\sigma \approx 1.5~{\rm
MAD}$, assuming the samples are Gaussian distributed) of the samples and find
that the typical velocity \emph{precision} from measuring the centroid of \Ha\ is between $2$--$10~\kms$ \todo{double check numbers}.

@@

\software{
The code used in this project is available from
\url{https://github.com/adrn/GaiaPairsFollowup} under the MIT open-source
software license.
This research utilized the following open-source \python\ packages:
    \package{Astropy} (\citealt{Astropy-Collaboration:2013}),
    \package{astroquery} (\citealt{Ginsburg:2016}),
    \package{ccdproc} (\citealt{Craig:2015}),
    \package{celerite} (\citealt{Foreman-Mackey:2017}),
    \package{IPython} (\citealt{Perez:2007}),
    \package{matplotlib} (\citealt{Hunter:2007}),
    \package{numpy} (\citealt{Van-der-Walt:2011}),
    \package{scipy} (\url{https://www.scipy.org/}),
    \package{sqlalchemy} (\url{https://www.sqlalchemy.org/})
This work additionally used the Gaia science archive
(\url{https://gea.esac.esa.int/archive/}).
}
